### 2023-10-09 main.tex
fix

\subsection{Steady state correlations and duality}\label{Subsection-ss-nonI}

@@

\section{Exact steady state and arbitrary correlations for the integrable chain}\label{sectionIntegrabiliy}

@@

\subsection{The integrable chain and the non-equilibrium steady state}

>>>>

\subsection{Duality for a boundary driven chain}\label{Subsection-ss-nonI}

@@

\section{Exact steady state and correlations for the integrable chain}\label{sectionIntegrabiliy}

@@

\subsection{Matrix product ansatz for the non-equilibrium steady state}
